\text{Additive drift with tail bounds}

### 2021-09-26 article.tex
fix english 2

\section{Time bounds for process with variable $\lambda$}
\cm
\subsection{Case when $\lambda$ is random value}
Consider the total progress $\Delta X$ by $T$ iterations. It is a sum of all progresses $\Delta X_i$ made in previous iteration
\[
    \Delta X = \sum_{i = 0}^{T} \Delta X_i
\]

By Vald's equality we have

@@

If ew assume that $E[\Delta X_i]$ is a constant or at least we can give relatively sharp bounds lower and upper bounds on it, then
\[
    E[\Delta X] = E\left[\sum_{i = 1}^{T} \Delta X_i\right] \thickapprox E[T] E[\Delta X_i].
\]

Let $\Lambda$ be the total cost, which is total number of fitness evaluations (the fitness evaluations in iteration $i$ equals $\lambda_i$). Since $\lambda$ is random variable, each $\lambda_i$ has the same expectation. Therefore, we have
\[
    E\left[\Lambda\right] = E\left[\sum_{i = 1}^{T} \lambda_i\right] = E[T] E[\lambda] \thickapprox \frac{E[\Delta X] E[\lambda]}{E[\Delta X_i]}
\]

If we denote $\vartheta_\lambda = \frac{E[\Delta X_i]}{E[\lambda]}$, which is the expected progress per fitness evaluation, then the previous equation is simplified to
\[
    E[\Lambda] \thickapprox \frac{E[\Delta X]}{\vartheta_\lambda}
\]
% $\vartheta_{\lambda, X_t} = \nu (\lambda, X_t)$

>>>>

\section{Time bounds for process with variable $\lambda$}
\cm
\subsection{Case when $\lambda$ is a random variable}
Consider the total progress $\Delta X$ made in $T$ iterations. It is a sum of all progresses $\Delta X_i$ made in each of $T$ iterations.
\[
    \Delta X = \sum_{i = 0}^{T} \Delta X_i
\]

By Wald's equality we have

@@

If we assume that $E[\Delta X_i]$ is a constant or at least we can give relatively sharp lower and upper bounds on it, then
\[
    E[\Delta X] = E\left[\sum_{i = 1}^{T} \Delta X_i\right] \thickapprox E[T] E[\Delta X_i].
\]

Let $\Lambda$ be the total cost, which is the total number of fitness evaluations (the fitness evaluations in iteration $i$ equals $\lambda_i$). Since $\lambda$ is a random variable, each $\lambda_i$ has the same expectation. Therefore, we have
\[
    E\left[\Lambda\right] = E\left[\sum_{i = 1}^{T} \lambda_i\right] = E[T] E[\lambda] \thickapprox \frac{E[\Delta X] E[\lambda]}{E[\Delta X_i]}
\]

If we denote $\vartheta_\lambda = \frac{E[\Delta X_i]}{E[\lambda]}$, which is the expected progress per fitness evaluation, then the previous equation is simplified to
\[
    E[\Lambda] \thickapprox \frac{E[\Delta X]}{\vartheta_\lambda}.
\]
% $\vartheta_{\lambda, X_t} = \nu (\lambda, X_t)$
